\section{Advantages of the System}
\begin{itemize}
    \item \textbf{Transparency:} Every project activity, payment, and rating is recorded on the blockchain, ensuring complete visibility and accountability.
    \item \textbf{Security:} Transactions are secured using cryptographic algorithms, preventing unauthorized modifications or data breaches.
    \item \textbf{Low Cost:} Eliminates high service fees associated with centralized freelancing platforms.
    \item \textbf{Faster Payments:} Automates fund transfers through smart contracts, minimizing payment delays.
    \item \textbf{Global Participation:} Enables freelancers and clients to collaborate globally without banking restrictions.
    \item \textbf{Decentralized Storage:} Utilizes IPFS to store project deliverables in a tamper-proof and distributed manner.
    \item \textbf{Immutable Reputation:} On-chain reputation ensures long-term credibility for users.
\end{itemize}

\section{Limitations}
\begin{itemize}
    \item \textbf{Gas Fees Volatility:} Transaction costs may vary depending on blockchain congestion.
    \item \textbf{Technical Barrier:} Users require basic understanding of blockchain wallets and cryptocurrencies.
    \item \textbf{Limited Dispute Resolution:} Smart contracts cannot fully handle complex disputes without external arbitration.
    \item \textbf{Scalability Concerns:} High network load may affect transaction times during peak usage.
\end{itemize}

\section{Applications}
\begin{itemize}
    \item \textbf{Freelancing and Gig Economy:} Enables fair and transparent work engagements.
    \item \textbf{Crowdsourcing Platforms:} Supports decentralized task allocation and reward mechanisms.
    \item \textbf{Corporate Outsourcing:} Can be adapted for enterprise-level project management and contracting.
    \item \textbf{Peer-to-Peer Marketplaces:} Useful in creating marketplaces without intermediaries.
\end{itemize}

\section{Summary}
This chapter summarized the strengths, weaknesses, and potential applications of the proposed system. The Decentralized Freelance Platform stands as a practical demonstration of how blockchain can redefine digital employment ecosystems by ensuring transparency, reducing costs, and fostering trust among participants.
