\chapter{Summary of Papers Referred (IEEE Format)}

This appendix summarizes the key research works and ideas that served as the foundation for the development of this project. Each paper contributed conceptual or technical insights toward implementing a decentralized, blockchain-based freelancing platform.

\begin{itemize}
    \item \textbf{Deshmukh et al. (2020):} Proposed a decentralized freelancing model using Ethereum smart contracts to automate payment handling and dispute management. The idea of trustless escrow and smart contract enforcement directly influenced the payment module of our platform.

    \item \textbf{Fraunhofer ICT Group (2018):} Analyzed the architecture of blockchain and smart contracts in digital marketplaces. This paper guided the design of our hybrid architecture combining on-chain automation with off-chain data handling.

    \item \textbf{Levy (2017):} Introduced a decentralized fundraising and freelancing network with token-based incentives and community governance. This inspired the concept of on-chain reputation and governance mechanisms in our system.

    \item \textbf{Pallam and Gore (2019):} Developed “Boomerang,” a blockchain-based freelance framework built on Hyperledger. Their emphasis on scalability and privacy influenced our hybrid storage model using IPFS and The Graph.

    \item \textbf{Chatterjee et al. (2015):} Discussed decentralized allocation schemes to enhance fairness and efficiency in freelance markets. Their analysis contributed to the design of equitable project bidding and milestone mechanisms.

    \item \textbf{Hald and Kinra (2019):} Examined blockchain’s impact on supply chain transparency and traceability. The same principles were applied to ensure transparency in freelancer–client interactions and transaction tracking.

    \item \textbf{Pourheidari et al. (2018):} Presented a case study on executing untrusted business logic on permissioned blockchains. Their insights informed the security and smart contract validation aspects of this project.

    \item \textbf{Wood (2013):} Introduced the Ethereum blockchain, providing the foundation for programmable contracts. This directly influenced our choice of Ethereum-compatible smart contracts.

    \item \textbf{Olariu et al. (2024):} Proposed Trust and Reputation as a Service (TRaaS), highlighting the need for decentralized reputation management. This work guided our design of immutable on-chain rating systems.

    \item \textbf{Nakamoto (2008):} Introduced Bitcoin, the first peer-to-peer decentralized currency. This foundational idea of decentralization and cryptographic validation inspired the overall direction of our system architecture.
\end{itemize}

Each of these studies collectively contributed to the development of a transparent, secure, and efficient decentralized freelancing ecosystem implemented in this project.
