\section{Motivation}
The global freelancing sector has become one of the most rapidly growing segments of the digital economy, reshaping how people engage with work in a borderless environment. Platforms such as Upwork, Fiverr, and Freelancer have enabled millions of individuals to connect with clients worldwide. Despite their effectiveness, these platforms are centralized and governed by third-party authorities that regulate user accounts, payments, and dispute mechanisms. 

This centralization introduces multiple drawbacks such as high platform fees, delayed payments, restricted access in certain regions, and limited transparency. For freelancers, these issues translate into reduced earnings and limited control, while clients face increased costs and lower confidence in fair dispute resolutions. These shortcomings motivate the development of a decentralized system that can provide fairness, transparency, and autonomy through blockchain technology.

\section{Problem Definition}
Traditional freelance marketplaces rely on centralized systems for financial transactions and contract enforcement. This results in a lack of transparency, dependency on intermediaries, and possible manipulation in payment and review processes. Moreover, centralized databases pose security risks such as data breaches and single points of failure. 

The proposed project aims to address these problems by designing a blockchain-based freelance platform that functions in a decentralized, transparent, and secure manner. The system ensures that project contracts and payments are governed automatically through smart contracts, eliminating the need for a trusted intermediary.

\section{Objectives}
The main objectives of this project are:
\begin{itemize}
    \item To develop a decentralized freelancing platform using blockchain technology.
    \item To enable secure and automated escrow-based payments using Ethereum smart contracts.
    \item To reduce the dependency on centralized intermediaries and eliminate high transaction fees.
    \item To ensure transparency, immutability, and trust in all transactions between clients and freelancers.
    \item To store project deliverables securely using decentralized storage systems such as IPFS.
    \item To provide a user-friendly web interface for job posting, bidding, and milestone management.
\end{itemize}

\section{Scope of the Project}
The proposed decentralized freelance platform is intended for use by both clients and freelancers seeking transparent and secure project collaborations. It offers a web-based user interface integrated with blockchain wallets such as MetaMask to enable smooth crypto transactions. The platform supports milestone-based project execution, escrow mechanisms, and on-chain reputation tracking. 

The scope of the project is limited to implementing and validating the system prototype on Ethereum-compatible test networks such as Polygon/Sepolia. Future extensions may include the integration of AI-based matching algorithms, DAO-based arbitration, and fiat payment gateways to improve scalability and usability.

\section{Organization of the Report}
This report is structured as follows:
\begin{itemize}
    \item Chapter 1 introduces the project motivation, problem statement, objectives, and scope.
    \item Chapter 2 presents a detailed literature survey of existing research and systems related to decentralized freelancing.
    \item Chapter 3 describes the software requirements specification (SRS), outlining functional, non-functional, and system requirements.
    \item Chapter 4 discusses the system design and architecture, including the use of blockchain, IPFS, and smart contracts.
    \item Chapter 5 presents the comparative analysis between centralized and decentralized platforms.
    \item Chapter 6 concludes the report with findings, limitations, and future enhancements.
\end{itemize}
