\newpage
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{9}

\bibitem{ref1}
P. Deshmukh, S. Kalwaghe, A. Appa, and A. Pawar, 
“Decentralised freelancing using Ethereum Blockchain,” 
in \textit{Proceedings of the IEEE International Conference on Communication and Signal Processing (ICCSP)}, 2020.

\bibitem{ref2}
Fraunhofer ICT Group, 
\textit{Blockchain and Smart Contracts}, 
Fraunhofer ICT Group, Apr. 2018.

\bibitem{ref3}
A. Levy, 
“A decentralized fundraising and freelancing network,” 
\textit{Whitepaper Revision 1.00 — Draft for Community Review}, Oct. 2017.

\bibitem{ref4}
B. Pallam and M. M. Gore, 
“Boomerang: Blockchain-based freelance paradigm on Hyperledger,” 
in \textit{Proceedings of the 10th International Conference on Computing, Communication and Networking Technologies (ICCCNT)}, Jul. 2019.

\bibitem{ref5}
A. Chatterjee, L. R. Varshney, and S. Vishwanath, 
“Work capacity of freelance markets: Fundamental limits and decentralized schemes,” 
in \textit{Proceedings of the IEEE INFOCOM}, Hong Kong, Jan. 2015.

\bibitem{ref6}
S. Nakamoto, 
“Bitcoin: A peer-to-peer electronic cash system,” 
2008.

\bibitem{ref7}
K. S. Hald and A. Kinra, 
“How the blockchain enables and constrains supply chain performance,” 
\textit{International Journal of Physical Distribution \& Logistics Management}, Feb. 2019.

\bibitem{ref8}
G. Wood, 
“Ethereum: A secure decentralised generalised transaction ledger,” 
\textit{Ethereum Foundation, EIP-150 Revision 3}, 2013.

\bibitem{ref9}
S. Olariu, R. Mukkamala, and M. Aljohani, 
“Towards trust and reputation as a service in a blockchain-based decentralized marketplace,” 
in \textit{IEEE Conference Proceedings}, 2024.

\bibitem{ref10}
V. Pourheidari, S. Rouhani, and R. Deters, 
“A case study of execution of untrusted business on permissioned blockchain,” 
in \textit{IEEE Conference on Blockchain}, Halifax, Canada, 2018.

\end{thebibliography}
