\section{Introduction}
This chapter presents the results and performance evaluation of the proposed Decentralized Freelance Platform. The system is compared with traditional centralized freelancing platforms based on parameters such as cost efficiency, transparency, security, settlement speed, and global accessibility.

\section{Comparative Analysis}
The proposed system was compared with existing centralized platforms such as Upwork and Fiverr. The following observations were made:

\begin{itemize}
    \item \textbf{Cost Efficiency:} Traditional platforms charge service fees ranging from 10–20\%, significantly reducing freelancer earnings. In contrast, the decentralized model incurs only minimal blockchain gas fees.
    \item \textbf{Transparency:} All payments, milestones, and interactions are stored immutably on the blockchain, eliminating the risk of hidden fees or data manipulation.
    \item \textbf{Security:} Smart contracts ensure tamper-proof and verifiable transactions secured by cryptography.
    \item \textbf{Settlement Speed:} Payments are automated through smart contracts and released immediately upon approval, avoiding manual delays.
    \item \textbf{Global Accessibility:} Users can participate globally using cryptocurrency wallets without regional banking restrictions.
    \item \textbf{Data Integrity:} Decentralized IPFS storage ensures no single point of failure or unauthorized access.
\end{itemize}

\section{Tabular Comparison}
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|l|X|X|}
\hline
\textbf{Parameter} & \textbf{Existing System (Centralized)} & \textbf{Proposed System (Decentralized)} \\
\hline
Service Fee & 10--20\% per project & Minimal network gas fee only \\
\hline
Payment Processing & Delayed by intermediaries & Instant release via smart contracts \\
\hline
Trust Mechanism & Platform-controlled & Code-enforced and transparent \\
\hline
Data Storage & Centralized databases & Decentralized IPFS \\
\hline
Accessibility & Limited to banking regions & Global, crypto-based \\
\hline
Security & Vulnerable to hacks and data breaches & Cryptographically secured blockchain \\
\hline
Reputation Management & Platform-managed and modifiable & Immutable, on-chain ratings \\
\hline
\end{tabularx}
\end{center}


\section{System Performance}
During testing on the Polygon test network, the following performance metrics were observed:
\begin{itemize}
    \item Average transaction confirmation time: 4–6 seconds.
    \item Smart contract deployment cost: approximately 0.002 ETH (test network equivalent).
    \item IPFS file upload latency: under 3 seconds for files under 5 MB.
    \item User transaction success rate: 98\%.
\end{itemize}

The results validate that the proposed decentralized platform performs efficiently while ensuring high reliability and transparency across operations.
