\section{Project Scope}
The proposed Decentralized Freelance Platform aims to build a transparent, secure, and efficient freelancing ecosystem using blockchain technology. It replaces the traditional centralized intermediaries with smart contracts and decentralized storage, ensuring trustless and tamper-proof project transactions. The system supports essential freelance operations such as job posting, bidding, milestone tracking, escrow payments, and reputation management through blockchain automation.

\section{Functional Requirements}
\begin{itemize}
    \item \textbf{User Registration and Authentication:} Users (clients and freelancers) can create accounts and connect their digital wallets (MetaMask) to the platform.
    \item \textbf{Job Posting and Bidding:} Clients can post project requirements, and freelancers can submit bids and proposals.
    \item \textbf{Smart Contract Creation:} Upon bid acceptance, a smart contract is generated on the Ethereum network to manage project terms.
    \item \textbf{Escrow Management:} Client funds are securely held in escrow within the smart contract and automatically released after successful milestone completion.
    \item \textbf{Milestone Tracking:} Projects are divided into multiple milestones to ensure transparent progress and conditional payments.
    \item \textbf{File Storage:} Project files and deliverables are stored using IPFS, ensuring decentralized and tamper-proof file storage.
    \item \textbf{Reputation System:} Ratings and feedback are stored on-chain to maintain transparency and credibility across users.
    \item \textbf{Transaction Verification:} All transactions and contract events are recorded immutably on the blockchain and retrievable for auditing.
\end{itemize}

\section{Non-functional Requirements}
\begin{itemize}
    \item \textbf{Security:} The platform ensures cryptographic data integrity through SHA-256 hashing and secure wallet-based authentication.
    \item \textbf{Transparency:} Every project activity, payment, and review is publicly verifiable on the blockchain.
    \item \textbf{Scalability:} The architecture supports hybrid on-chain/off-chain operations to manage large data volumes efficiently.
    \item \textbf{Usability:} The user interface is built with React.js and Node.js for an intuitive and responsive user experience.
    \item \textbf{Availability:} Decentralized infrastructure ensures high system uptime and resilience against single-point failures.
    \item \textbf{Performance:} The system is optimized for quick querying using The Graph protocol to fetch blockchain data efficiently.
\end{itemize}

\section{System Requirements}
\subsection{Hardware Requirements}
\begin{itemize}
    \item Minimum 8 GB RAM and Quad-core Processor
    \item Stable internet connection for blockchain synchronization
    \item Minimum 2 GB storage for project data and dependencies
\end{itemize}

\subsection{Software Requirements}
\begin{itemize}
    \item Operating System: Windows, Linux, or macOS
    \item Frontend: React.js
    \item Backend: Node.js
    \item Blockchain: Ethereum/Polygon network
    \item Smart Contract Language: Solidity
    \item Database: IPFS (for file storage)
    \item Middleware: The Graph protocol
    \item Wallet Integration: MetaMask
\end{itemize}

\section{Assumptions and Dependencies}
\begin{itemize}
    \item Users possess basic understanding of cryptocurrency wallets and blockchain transactions.
    \item Transactions depend on the availability of Ethereum test networks (such as Goerli or Polygon Mumbai).
    \item Network gas fees may vary depending on blockchain congestion.
    \item Reliable internet connectivity is required for interacting with decentralized networks.
\end{itemize}
